Outbreak Threshold Detection

### 2023-03-07 notebooks/Julia/simulation-detection.qmd
Try using AlgebraOfGraphics for single SIR plot Wanted to try using AOG as uses ggplot2 style syntax. Seems like it's pretty doable for a simple plot, but would require I create a large dataframe for the multiple simulations, rather than using an array. Given Julia's col-major, I'm not sure what implications this has for speed, but I'm guessing this doesn't have that big an effect.

```{julia}
using JumpProcesses, StochasticDiffEq, DifferentialEquations, LinearAlgebra
using Catalyst, Random, Statistics, DataFrames, CairoMakie, ProgressMeter
using BenchmarkTools

CairoMakie.activate!()
```

@@

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), gillespie_jumps...)
sol = solve(jump_prob, SSAStepper())
sol_array = zeros(5, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:4, :], dims = 1)
```

```{julia}
fig = Figure()
ax = Axis(
    fig[1, 1],
    xlabel = "Time",
    ylabel = "Number"
)

lines!(ax, sol.t, sol_array[1, :], linewidth = 3, label = "S(t)")
lines!(ax, sol.t, sol_array[2, :], linewidth = 3, label = "E(t)")
lines!(ax, sol.t, sol_array[3, :], linewidth = 3, label = "I(t)")
lines!(ax, sol.t, sol_array[4, :], linewidth = 3, label = "R(t)")
lines!(ax, sol.t, sol_array[5, :], linewidth = 3, label = "N(t)")

fig
```

>>>>

```{julia}
using JumpProcesses, StochasticDiffEq, DifferentialEquations, LinearAlgebra
using Catalyst, Random, Statistics, DataFrames, CairoMakie, AlgebraOfGraphics
using BenchmarkTools, ProgressMeter

CairoMakie.activate!()
set_aog_theme!()
```

@@

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), gillespie_jumps...)
sol = solve(jump_prob, SSAStepper())
sol_array = zeros(6, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:4, :], dims = 1)
sol_array[6, :] = sol.t;
```

```{julia}
sol_df = DataFrame(Tables.table(sol_array'))

rename!(sol_df, :Column1 => :S, :Column2 => :E, :Column3 => :I, :Column4 => :R, :Column5 => :N, :Column6 => :time)

stacked_df = stack(sol_df, [:S, :E, :I, :R, :N])
```

```{julia}
colors = ["dodgerblue4", "firebrick3", "chocolate2", "green", "purple"]
sir_plot = data(stacked_df) *
    mapping(
        :time => "Time (Years)", :value => "Number",
        color = :variable => sorter("S", "E", "I", "R", "N") => "State"
    ) *
    visual(Lines, linewidth = 4)
draw(sir_plot; palettes = (; color = colors))
```
